Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-26 main.tex
20180826

\section{Introduction} \label{intro}

As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being. Photovoltaic (PV) energy has received a significant attention since it is unlimited and easy to be scaled up. Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation systems have been deployed into many practical applications. However, PV arrays are sensitive to shading and PV cell's fault or aging. This implies that when interconnection of PV cells or modules do not have identical properties or experience different conditions from one another. the PV array is in mismatch condition. The photovoltaic arrays under mismatched conditions will accelerate the aging and heating of PV cells and cause a short circuit of photovoltaic cells to further damage the PV array. In order to avoid mismatch condition damage PV cells, we propose an algorithm that can reconfigure photovoltaic arrays to avoid mismatch damage and maximize generated power.

>>>>

\section{Introduction} \label{intro}
As fossil energy is constantly depleted and increasing a serious pollution problem for the environment, research and utilization on a green and renewable energy have become necessary to support human existence and guarantee a sustainable human development.
%As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being. 
Photovoltaic (PV) energy has received a significant attention since it is unlimited and easy to be scaled up. Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation systems have been deployed into many practical applications. However, PV arrays are sensitive to shading and PV cell's fault or aging. This implies that when interconnection of PV cells or modules do not have identical properties or experience different conditions from one another. the PV array is in mismatch condition. The photovoltaic arrays under mismatched conditions will accelerate the aging and heating of PV cells and cause a short circuit of photovoltaic cells to further damage the PV array. In order to avoid mismatch condition damage PV cells, we propose an algorithm that can reconfigure photovoltaic arrays to avoid mismatch damage and maximize generated power.
